An event-sourced and distributed database with IPLD and materialized views

### 2019-09-19 draft.tex
couple more linkages
Signed-off-by: andrew <andrew@textile.io>
remove placeholder
Signed-off-by: andrew <andrew@textile.io>
more fiddling
Signed-off-by: andrew <andrew@textile.io>

\begin{figure}
  \includegraphics[width=\linewidth]{boat.jpg}
  \caption{This is really a code embed.}
  \label{fig:boat1}
\end{figure}

@@

    // Sig is a cryptographic signature of Event and Refs
    // created with the Log's private key.
    Sig() []byte
}

// Event represents the content of an update.
// Note: In practice, this is encrypted with the Read key.
type Event interface {
    ipld.Node

@@

    // Decrypt is a helper function that decrypts Body
    // with a key in Header.
    Decrypt() (ipld.Node, error)
}

// EventHeader contains Event metadata.
type EventHeader interface {
    ipld.Node

@@

Much like IPFS Peers, Logs are identified on the network with addresses, or more specifically, with multiaddresses [ref]. Here we introduce IPEL, or Interplanetary Event Log, as a new protocol tag to be used when composing Log multiaddresses (see inset). In practice, to reach a Log via it’s IPEL multiaddress, it must be encapsulated in an IPFS Peer multiaddress (see inset).

@@

Followers are represented as additional addresses, meaning that a Log address book may contain multiple multiaddresses for a single Log (see inset).

@@

\begin{strip}
\begin{tcolorbox}[title=Log Multiaddress]
"/ipel/12D3KooWC2zyCVron7AA34N6oKNtaXaZB51feG9rBkr7QbCcW8ab"
\end{tcolorbox}
\end{strip}

\begin{strip}
\begin{tcolorbox}[title=Log IPEL Multiaddress]
"/ip4/127.0.0.1/tcp/1234/p2p/12D..dwaA6Qe/ipel/12D..bCcW8ab"
\end{tcolorbox}
\end{strip}

\begin{strip}
\begin{tcolorbox}[title=Log Multiple Multiaddress]
[\\
  "/p2p/12D..dwaA6Qe/ipel/12D..bCcW8ab",\\
  "/p2p/12D..dJT6nXY/ipel/12D..bCcW8ab" // Follower\\
]
\end{tcolorbox}
\end{strip}

>>>>

@@

    // Sig is a cryptographic signature of Event and Refs
    // created with the Log's private key.
    Sig() []byte
}
\end{lstlisting}

\begin{lstlisting}
// Event represents the content of an update.
// Note: In practice, this is encrypted with the Read key.
type Event interface {
    ipld.Node

@@

    // Decrypt is a helper function that decrypts Body
    // with a key in Header.
    Decrypt() (ipld.Node, error)
}
\end{lstlisting}
\begin{lstlisting}
// EventHeader contains Event metadata.
type EventHeader interface {
    ipld.Node

@@

Much like IPFS Peers, Logs are identified on the network with addresses, or more specifically, with multiaddresses [ref]. Here we introduce IPEL, or Interplanetary Event Log, as a new protocol tag to be used when composing Log multiaddresses:\\

\tiny
\textbf\textit /ipel/12D3KooWC2zyCVron7AA34N6oKNtaXaZB51feG9rBkr7QbCcW8ab\\
\normalsize

In practice, to reach a Log via it’s IPEL multiaddress, it must be encapsulated in an IPFS Peer multiaddress:\\

\tiny
\textbf\textit /ip4/127.0.0.1/tcp/1234/p2p/12D..dwaA6Qe/ipel/12D..bCcW8ab\\
\normalsize

@@

Followers are represented as additional addresses, meaning that a Log address book may contain multiple multiaddresses for a single Log:

\begin{lstlisting}
[
  "/p2p/12D..dwaA6Qe/ipel/12D..bCcW8ab",
  "/p2p/12D..dJT6nXY/ipel/12D..bCcW8ab" // Follower
]
\end{lstlisting}

@@
